\textbf{\Large Computer Vision-based System for Impaired Human Vision Compensation}

### 2018-10-04 bare_conf.tex
some typos fixed, more text added.

The interface consists of a wearable forehead belt, integrating RGB and depth cameras, tactile feedback device and bone conductive headphones. Altough more expensive than standard ones, bone conductive headphones allow the user to perceive audio information from the surrounding environment, which is essential for the visually impaired people.

@@

The cornerstone of this project is the interface between the visually impaired person and the assistive technology. We are proposing a combination of audio and tactile feedback, which may improve the interaction between the assitive technology and the user. Similar interfaces were suggested by research communities earlier \cite{Zientara}, \cite{Poggi}, however, current knowledge on user preferences and evaluation of various options of tactile feedback (placement on the body, frequencies, strength, etc.) is limited.

@@

In this article we outlined an idea of complex computer vision-based sensor architecture, which can help to partially compensate impaired or lost human sight. Main advantages of therein suggested system are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via Internet connection, present the signal to the user by combined bone conductive headphone-tactile actuator, comparatively low cost and consequently increased potential availability of the device. The suggested system also integrates well with the main blind person's aid - the white cane. The hardware architecture can be used as the basis for various computer vision-based software modules, allowing to help visually impaired users in everyday routines (e.g. outdoor/indoor navigation, object/face recognition, obstacle detection, etc.). On the other side, due to remotelly conducted visual analysis, in some cases the suggested system may suffer from too large latency, its reliability depends on stability and quality of Internet connection.

>>>>

The interface consists of a wearable forehead belt, integrating RGB and depth cameras, tactile feedback device and bone conductive headphones. Although more expensive than standard ones, bone conductive headphones allow the user to perceive audio information from the surrounding environment, which is essential for the visually impaired people.

@@

The cornerstone of this project is the interface between the visually impaired person and the assistive technology. We are proposing a combination of audio and tactile feedback, which may improve the interaction between the assistive technology and the user. Similar interfaces were suggested by research communities earlier \cite{Zientara}, \cite{Poggi}, however, current knowledge on user preferences and evaluation of various options of tactile feedback (placement on the body, frequencies, strength, etc.) is limited.

@@

In this article we outlined an idea of complex computer vision-based sensor architecture, which can help to partially compensate impaired or lost human sight. Main advantages of therein suggested system are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via Internet connection, present the signal to the user by combined bone conductive headphone-tactile actuator, comparatively low cost and consequently increased potential availability of the device. The suggested system also supplements the main blind person's aid - the white cane. The hardware architecture can be used as the basis for various computer vision-based software modules, allowing to help visually impaired users in everyday routines (e.g. outdoor/indoor navigation, object/face recognition, obstacle detection, etc.). On the other side, due to remotelly conducted visual analysis, in some cases the suggested system may suffer from too large latency, its reliability depends on stability and quality of Internet connection. We are currently  implementing suggested the architecture into working prototype for preliminary evaluation by potential end users.
